% =====================================================================
% Список литературы
% =====================================================================
\begin{frame}{Литература (классические трекеры)}

\footnotesize
\begin{thebibliography}{99}

\bibitem{Rabiner1989}
  L.~R.~\textbf{Rabiner}.\\
  A tutorial on hidden Markov models and selected applications in
  speech recognition.\\
  \emph{Proc.\ IEEE} 77(2):257--286, 1989.

\bibitem{Dixon2005}
  S.~\textbf{Dixon}.\\
  Live Tracking of Musical Performances Using On-Line Time Warping.\\
  \emph{Proc.\ DAFx}, 2005.

\bibitem{Cont2010}
  A.~\textbf{Cont}.\\
  A Coupled Duration-Focused Architecture for Real-Time Music-to-Score
  Alignment.\\
  \emph{IEEE Trans.\ PAMI} 32(6):974--987, 2010.

\bibitem{Nakamura2015}
  E.~\textbf{Nakamura}, N.~Ono, S.~Sagayama.\\
  Real-time Audio-to-Score Alignment of Music Performances.\\
  \emph{IEEE/ACM TASLP}, 2015.

\bibitem{Mueller2007}
  M.~\textbf{Müller}.\\
  Information Retrieval for Music and Motion.\\
  Springer, 2007.

\end{thebibliography}

\end{frame}

\begin{frame}{Литература (RL и обучение)}

\footnotesize
\begin{thebibliography}{99}

\bibitem{Schulman2017}
  J.~\textbf{Schulman} et al.\\
  Proximal Policy Optimization Algorithms.\\
  \emph{arXiv:1707.06347}, 2017.

\bibitem{Schulman2016}
  J.~\textbf{Schulman} et al.\\
  High-Dimensional Continuous Control Using Generalized Advantage
  Estimation.\\
  \emph{ICLR}, 2016.

\bibitem{Sutton2018}
  R.~\textbf{Sutton}, A.~Barto.\\
  Reinforcement Learning: An Introduction (2nd ed.).\\
  MIT Press, 2018.

\bibitem{Jaques2017}
  N.~\textbf{Jaques} et al.\\
  Sequence Tutor: Conservative Fine-Tuning of Sequence Generation
  Models with KL-Control.\\
  \emph{ICML}, 2017.

\bibitem{Christiano2017}
  P.~\textbf{Christiano} et al.\\
  Deep Reinforcement Learning from Human Preferences.\\
  \emph{NeurIPS}, 2017.

\end{thebibliography}

\end{frame}

\begin{frame}{Литература (RL для музыки и датасеты)}

\footnotesize
\begin{thebibliography}{99}

\bibitem{Dorfer2018}
  M.~\textbf{Dorfer}, A.~Arzt, G.~Widmer.\\
  Learning to Listen, Read, and Follow: Score Following as a
  Reinforcement Learning Game.\\
  \emph{ISMIR}, 2018.

\bibitem{Peter2023}
  S.~\textbf{Peter} et al.\\
  Online Symbolic Music Alignment with Offline Reinforcement Learning.\\
  \emph{ISMIR}, 2023.

\bibitem{Jiang2020}
  N.~\textbf{Jiang} et al.\\
  RL-Duet: Online Music Accompaniment Generation Using Deep
  Reinforcement Learning.\\
  \emph{AAAI}, 2020.

\bibitem{Wu2024}
  Y.~\textbf{Wu} et al.\\
  Adaptive Accompaniment with ReaLchords.\\
  \emph{NeurIPS}, 2024.

\bibitem{Foscarin2020}
  F.~\textbf{Foscarin} et al.\\
  ASAP: a Dataset of Aligned Scores and Performances for Piano
  Transcription.\\
  \emph{ISMIR}, 2020.

\bibitem{Hawthorne2018}
  C.~\textbf{Hawthorne} et al.\\
  Enabling Factorized Piano Music Modeling and Generation with the
  MAESTRO Dataset.\\
  \emph{ICLR}, 2018.

\end{thebibliography}

\end{frame}
